BioTime

### 2019-04-24 biotime.Rmd
Make id matching for trait data a function.

##Elton Traits
Get id's for the Elton Bird trait data
```{r}
sci_names <-  by_name(unique(bird_trait$scientific), "itis") %>%
  drop_na(acceptedNameUsageID) %>%
  #get original specid so we can figure out how many don't have matches
  left_join(bird_trait %>% select(specid, scientific), by = c("input" = "scientific")) %>%
  mutate(match_type = "scientific")

@@

and 605 species without an ID
```{r}
biotime_data %>%
  filter(taxa == "Birds") %>%
  select(id, matchingName) %>%
  distinct() %>%
  filter(is.na(id)) %>%
  dim()
```

Are there any studies for which we have trait data for all species?
```{r}
#join trait and biotime data
bird_data <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  rowid_to_column("row") %>%
  left_join(bird_trait_data %>% 
              select(), 
            na_matches = "never")

coverage <- bird_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(id))/n()) %>%
  arrange(desc(perc))

>>>>

##Elton Traits
Get id's for the Elton Bird trait data

```{r}
get_trait_ids <- function(data, provider, id, common = TRUE){
  #id <- lazyeval::as_name(id)
  sci_match <-  by_name(unique(data$scientific), provider) %>%
    drop_na(acceptedNameUsageID) %>%
    #get original specid so we can figure out ho w many don't have matches
    left_join(data %>% select_(id, "scientific"), by = c("input" = "scientific")) %>%
    mutate(match_type = "scientific")

  if(common){
    com_names <- data %>% 
      #the id argument should be inplace of specid, but it doesn't work for some reason
      filter(!specid %in% sci_match$specid) %>%
      pull(english) %>%
      unique() %>%
      by_common("itis") %>%
      #mutate(match_type = "common")
      #filter(taxonRank == "species") %>% #only want ID's to species, since that's the level of the trait data
      drop_na(acceptedNameUsageID) %>%
      left_join(bird_trait %>% select_(id, "english"), by = c("input" = "english"))%>%
      mutate(match_type = "common")

    #there are both sci and common names, only want common name 
    return(bind_rows(sci_match, com_names))
  }else{ return(sci_match)}
}

test <- get_trait_ids(bird_trait, "itis", "specid")
test_mamm <- get_trait_ids(mamm_trait, "itis", "msw3_id", FALSE)

```{r}
sci_names <-  by_name(unique(bird_trait$scientific), "itis") %>%
  drop_na(acceptedNameUsageID) %>%
  #get original specid so we can figure out how many don't have matches
  left_join(bird_trait %>% select(specid, scientific), by = c("input" = "scientific")) %>%
  mutate(match_type = "scientific")

@@

and 605 bird species without an ID, 657 total species
```{r}
biotime_data %>%
  #filter(taxa == "Birds") %>%
  select(id, matchingName) %>%
  distinct() %>%
  filter(is.na(id)) %>%
  dim()
```

Are there any studies for which we have trait data for all species?
```{r}
#join trait and biotime data
bird_data <- biotime_data %>%
  #filter(taxa == "Birds") %>%
  left_join(bird_trait_data, by = "id",
            na_matches = "never")

coverage <- bird_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(specid))/n()) %>%
  arrange(desc(perc))
